Databrary: A digital data library for sharing research video

### 2015-01-22 jcdl-15/paper.tex
add a possible section
though maybe it's not overloading
Reflow only

Video and audio recordings play a key role in many areas of research, especially in psychology, linguistics, education, ethnography, and ethology.
Video documents experimental procedures or behaviors, conveys ideas, provides examples for teaching and scientific communication, and serves as a rich primary data source for later analysis.
Unfortunately, in standard practice, the use of video data is restricted to the researchers who collect them, due largely to the perceived requirements around privacy restrictions.
The goal of the Databrary project is to create tools that allow video data to be documented, organized, and shared so that other researchers can discover and re-purpose them for their own research interests.
Accordingly, Databrary, with an initial focus on research in developmental psychology and related fields, has created a web-based library to accommodate the storage and organization of video data, capture contextual information necessary for re-use, and standardize across datasets without placing undue burden on data contributors.
In this paper, we discuss the design and technical challenges of the system and describe some findings and structural solutions to these challenges. The larger discussion involving research data repositories and the role of libraries in automating and facilitating access to research data well after its original use is very much active and ongoing \cite{Castelli_etal_2013, Nielson_Hjørland_2014, Macmillan_2014}. While Databrary is a model for tackling some of the challenges there, the scope of this paper focuses more on how we handle research data of a specific format and from a specific discipline, with implications for the future of data cataloging and reuse in other contexts.

@@

>>>>

Video and audio recordings play a key role in many areas of research, especially in psychology, linguistics, education, ethnography, and ethology.
Video documents experimental procedures or behaviors, conveys ideas, provides examples for teaching and scientific communication, and serves as a rich primary data source for later analysis.
Unfortunately, in standard practice, the use of video data is restricted to the researchers who collect them, due largely to the perceived requirements around privacy restrictions.
The goal of the Databrary project is to create tools that allow video data to be documented, organized, and shared so that other researchers can discover and re-purpose them for their own research interests.
Accordingly, Databrary, with an initial focus on developmental psychology and related fields, has created a web-based library to accommodate the storage and organization of video data, capture contextual information necessary for re-use, and standardize across datasets without placing undue burden on data contributors.
In this paper, we discuss the design and technical challenges of the system and describe some findings and structural solutions to these challenges.
The larger discussion involving research data repositories and the role of libraries in automating and facilitating access to research data well after its original use is very much active and ongoing \cite{Castelli_etal_2013, Nielson_Hjørland_2014, Macmillan_2014}.
While Databrary is a model for tackling some of the challenges there, the scope of this paper focuses more on how we handle research data of a specific format and from a specific discipline, with implications for the future of data cataloging and reuse in other contexts.

@@

\section{Implications for Digital Libraries}
%%dg this might or might not be valuable but I am wondering if this is a section that might help draw all the pieces together. Or maybe this just boils down to a sentence or two in the next steps or conclusions
